---
title: "Assignment 4 - Tables"
author: "Emily Starer"
format: html
editor: visual
---

## Summary

The data is advertising media data. The data is from actual advertising campaigns. The data is represented in a table to have as a benchmarking documents for future media activation . The table represents different clients across Consideration campaigns. The columns in the table represent different KPIs used to measure media: Impressions, Clicks, CTR, Sales and CVR. I formatted the table to look at one specific tactic and then the rows represent each client so that it is easy to compare tactics across clients.

## Input Data Source

```{r}
#| echo: false
library(knitr)
library(DT)
library(tidyverse)
library(dbplyr)
```

```{r}
#read in data
library(readr)
media <- read.csv("mediadata.csv") 
head(media)
```

## Build Table

```{r}
#Consideration Table 

#grouping by Consideration Tactic
media_consid <- media %>% filter(media$Tactic == "Consideration")

#aggregate by Client 
media_consid <- media_consid %>% group_by(Client, Tactic) %>%
                                  summarize (Impressions = sum(Imps),
                                             Click = sum(Clicks),
                                             CTR = ((Click / Impressions)*100),
                                             Sales_Conversions = sum(Conversions),
                                             CVR =  ((Sales_Conversions / Impressions)*100))
media_consid
                                                                                        
```

```{r}
tbl_mediac_consid <- media_consid %>%
                    select (Client, Impressions, Click, CTR, Sales_Conversions, CVR) %>%
                    datatable (colnames= c("Client",
                                      "Impressions",
                                       "Clicks",
                                       "CTR",
                                       "Sales",
                                       "CVR"))%>%
                    formatRound(columns = c(2,3,5),
                                          digits = 0)%>%
                    formatPercentage(columns = c(4,6),
                                     digits = 1)

tbl_mediac_consid
```
